---
Title: "Spatial subsampling with semivariograms"
author: "Alyssa Willson"
date: "2024-04-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
load('../data/processed/mean_STEPPS.RData')
source('../R/funs.R')
```

```{r, include = FALSE}
# Indexing by cell number
x_ind <- seq(from = 1, to = length(x), by = 1)
y_ind <- seq(from = 1, to = length(y), by = 1)

# Melt with indices instead of distances
ash_melt <- melt_array(taxon_mat = ash,
                       x = x_ind, y = y_ind, time = time,
                       col_names = c('x', 'y', 'time', 'ash'))
beech_melt <- melt_array(taxon_mat = beech,
                         x = x_ind, y = y_ind, time = time,
                         col_names = c('x', 'y', 'time', 'beech'))
birch_melt <- melt_array(taxon_mat = birch,
                         x = x_ind, y = y_ind, time = time,
                         col_names = c('x', 'y', 'time', 'birch'))
elm_melt <- melt_array(taxon_mat = elm,
                       x = x_ind, y = y_ind, time = time,
                       col_names = c('x', 'y', 'time', 'elm'))
hemlock_melt <- melt_array(taxon_mat = hemlock,
                           x = x_ind, y = y_ind, time = time,
                           col_names = c('x', 'y', 'time', 'hemlock'))
maple_melt <- melt_array(taxon_mat = maple,
                         x = x_ind, y = y_ind, time = time,
                         col_names = c('x', 'y', 'time', 'maple'))
oak_melt <- melt_array(taxon_mat = oak,
                       x = x_ind, y = y_ind, time = time,
                       col_names = c('x', 'y', 'time', 'oak'))
other_conifer_melt <- melt_array(taxon_mat = other_conifer,
                                 x = x_ind, y = y_ind, time = time,
                                 col_names = c('x', 'y', 'time', 'other_conifer'))
other_hardwood_melt <- melt_array(taxon_mat = other_hardwood,
                                  x = x_ind, y = y_ind, time = time,
                                  col_names = c('x', 'y', 'time', 'other_hardwood'))
pine_melt <- melt_array(taxon_mat = pine,
                        x = x_ind, y = y_ind, time = time,
                        col_names = c('x', 'y', 'time', 'pine'))
spruce_melt <- melt_array(taxon_mat = spruce,
                          x = x_ind, y = y_ind, time = time,
                          col_names = c('x', 'y', 'time', 'spruce'))
tamarack_melt <- melt_array(taxon_mat = tamarack,
                            x = x_ind, y = y_ind, time = time,
                            col_names = c('x', 'y', 'time', 'tamarack'))

```

# Purpose

This document extends the analysis of spatial autocorrelation from the document titled Testing_spatial_subsampling.Rmd to the statistical analysis of spatial correlations with semivariograms. Instead of just visually assessing the spatial autocorrelation in the reconstructions, we can fit empirical variograms to the reconstructions at each time step for each taxon.

# Semivariances

First, I used the `semivariogram` function from the `gstat` package to fit spherical, exponential, and Gaussian variograms to each taxon at each time period. This function returns the semivariances of the relative abundances, as well as the sill, nugget, and range parameter estimates. The range is an estimate of how far away the grid cells need to be to be considered independent. The ratio of nugget:sill is an indicator of the strength of spatial dependence in the relative abundance, with high ratio (>75%) indicative of low spatial dependence.

Since I replaced the x-y distances with cell number, the distance and range can be interpreted as number of cells in the following analysis.

My expectation is that of these three options, the Guassian variogram will be the best fit because this is the closest to the nugget used for model fitting, but the actual nugget is an inverse power law kernel, which I believe is the same as the powered exponential kernel.

```{r}
ash_spherical_params <- matrix(, nrow = length(time), ncol = 4)
ash_exponential_params <- matrix(, nrow = length(time), ncol = 4)
ash_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(ash_melt,
                       time == t,
                       !is.na(ash))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$ash,
                                model = 'spherical')
  ash_spherical_params[i,1] <- t
  ash_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$ash,
                                model = 'exponential')
  ash_exponential_params[i,1] <- t
  ash_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$ash,
                                model = 'gaussian')
  ash_gaussian_params[i,1] <- t
  ash_gaussian_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
beech_spherical_params <- matrix(, nrow = length(time), ncol = 4)
beech_exponential_params <- matrix(, nrow = length(time), ncol = 4)
beech_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(beech_melt,
                       time == t,
                       !is.na(beech))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$beech,
                                model = 'spherical')
  beech_spherical_params[i,1] <- t
  beech_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$beech,
                                model = 'exponential')
  beech_exponential_params[i,1] <- t
  beech_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$beech,
                                model = 'gaussian')
  beech_gaussian_params[i,1] <- t
  beech_gaussian_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
birch_spherical_params <- matrix(, nrow = length(time), ncol = 4)
birch_exponential_params <- matrix(, nrow = length(time), ncol = 4)
birch_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(birch_melt,
                       time == t,
                       !is.na(birch))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$birch,
                                model = 'spherical')
  birch_spherical_params[i,1] <- t
  birch_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$birch,
                                model = 'exponential')
  birch_exponential_params[i,1] <- t
  birch_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$birch,
                                model = 'gaussian')
  birch_gaussian_params[i,1] <- t
  birch_gaussian_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
elm_spherical_params <- matrix(, nrow = length(time), ncol = 4)
elm_exponential_params <- matrix(, nrow = length(time), ncol = 4)
elm_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(elm_melt,
                       time == t,
                       !is.na(elm))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$elm,
                                model = 'spherical')
  elm_spherical_params[i,1] <- t
  elm_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$elm,
                                model = 'exponential')
  elm_exponential_params[i,1] <- t
  elm_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$elm,
                                model = 'gaussian')
  elm_gaussian_params[i,1] <- t
  elm_gaussian_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
hemlock_spherical_params <- matrix(, nrow = length(time), ncol = 4)
hemlock_exponential_params <- matrix(, nrow = length(time), ncol = 4)
hemlock_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(hemlock_melt,
                       time == t,
                       !is.na(hemlock))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$hemlock,
                                model = 'spherical')
  hemlock_spherical_params[i,1] <- t
  hemlock_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$hemlock,
                                model = 'exponential')
  hemlock_exponential_params[i,1] <- t
  hemlock_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$hemlock,
                                model = 'gaussian')
  hemlock_gaussian_params[i,1] <- t
  hemlock_gaussian_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
maple_spherical_params <- matrix(, nrow = length(time), ncol = 4)
maple_exponential_params <- matrix(, nrow = length(time), ncol = 4)
maple_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(maple_melt,
                       time == t,
                       !is.na(maple))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$maple,
                                model = 'spherical')
  maple_spherical_params[i,1] <- t
  maple_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$maple,
                                model = 'exponential')
  maple_exponential_params[i,1] <- t
  maple_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$maple,
                                model = 'gaussian')
  maple_gaussian_params[i,1] <- t
  maple_gaussian_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
oak_spherical_params <- matrix(, nrow = length(time), ncol = 4)
oak_exponential_params <- matrix(, nrow = length(time), ncol = 4)
oak_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(oak_melt,
                       time == t,
                       !is.na(oak))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$oak,
                                model = 'spherical')
  oak_spherical_params[i,1] <- t
  oak_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$oak,
                                model = 'exponential')
  oak_exponential_params[i,1] <- t
  oak_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$oak,
                                model = 'gaussian')
  oak_gaussian_params[i,1] <- t
  oak_gaussian_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
other_conifer_spherical_params <- matrix(, nrow = length(time), ncol = 4)
other_conifer_exponential_params <- matrix(, nrow = length(time), ncol = 4)
other_conifer_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(other_conifer_melt,
                       time == t,
                       !is.na(other_conifer))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$other_conifer,
                                model = 'spherical')
  other_conifer_spherical_params[i,1] <- t
  other_conifer_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$other_conifer,
                                model = 'exponential')
  other_conifer_exponential_params[i,1] <- t
  other_conifer_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$other_conifer,
                                model = 'gaussian')
  other_conifer_gaussian_params[i,1] <- t
  other_conifer_gaussian_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
other_hardwood_spherical_params <- matrix(, nrow = length(time), ncol = 4)
other_hardwood_exponential_params <- matrix(, nrow = length(time), ncol = 4)
other_hardwood_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(other_hardwood_melt,
                       time == t,
                       !is.na(other_hardwood))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$other_hardwood,
                                model = 'spherical')
  other_hardwood_spherical_params[i,1] <- t
  other_hardwood_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$other_hardwood,
                                model = 'exponential')
  other_hardwood_exponential_params[i,1] <- t
  other_hardwood_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$other_hardwood,
                                model = 'gaussian')
  other_hardwood_gaussian_params[i,1] <- t
  other_hardwood_gaussian_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
pine_spherical_params <- matrix(, nrow = length(time), ncol = 4)
pine_exponential_params <- matrix(, nrow = length(time), ncol = 4)
pine_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(pine_melt,
                       time == t,
                       !is.na(pine))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$pine,
                                model = 'spherical')
  pine_spherical_params[i,1] <- t
  pine_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$pine,
                                model = 'exponential')
  pine_exponential_params[i,1] <- t
  pine_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$pine,
                                model = 'gaussian')
  pine_gaussian_params[i,1] <- t
  pine_gaussian_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
spruce_spherical_params <- matrix(, nrow = length(time), ncol = 4)
spruce_exponential_params <- matrix(, nrow = length(time), ncol = 4)
spruce_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(spruce_melt,
                       time == t,
                       !is.na(spruce))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$spruce,
                                model = 'spherical')
  spruce_spherical_params[i,1] <- t
  spruce_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$spruce,
                                model = 'exponential')
  spruce_exponential_params[i,1] <- t
  spruce_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$spruce,
                                model = 'gaussian')
  spruce_gaussian_params[i,1] <- t
  spruce_gaussian_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
tamarack_spherical_params <- matrix(, nrow = length(time), ncol = 4)
tamarack_exponential_params <- matrix(, nrow = length(time), ncol = 4)
tamarack_gaussian_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(tamarack_melt,
                       time == t,
                       !is.na(tamarack))
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$tamarack,
                                model = 'spherical')
  tamarack_spherical_params[i,1] <- t
  tamarack_spherical_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$tamarack,
                                model = 'exponential')
  tamarack_exponential_params[i,1] <- t
  tamarack_exponential_params[i,2:4] <- sv$snr
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$tamarack,
                                model = 'gaussian')
  tamarack_gaussian_params[i,1] <- t
  tamarack_gaussian_params[i,2:4] <- sv$snr
}
```

I performed a visual assessment for all taxa, but only Ash is shown. Based on the visual assessments, the Gaussian model is the best fit to the relative abundance reconstructions. We can now use the parameters from this model to make inference about the distance of spatial correlation and its strength.

Here are the distances after which grid cells are deemed independent (in number of grid cells, the "range" parameter):

```{r, echo = FALSE}
taxa <- c('Ash', 'Beech', 'Birch',
          'Elm', 'Hemlock', 'Maple',
          'Oak', 'Other conifer', 'Other hardwood',
          'Pine', 'Spruce', 'Tamarack')
Range <- c(mean(ash_gaussian_params[,4]), mean(beech_gaussian_params[,4]),
            mean(birch_gaussian_params[,4]), mean(elm_gaussian_params[,4]),
            mean(hemlock_gaussian_params[,4]), mean(maple_gaussian_params[,4]),
            mean(oak_gaussian_params[,4]), mean(other_conifer_gaussian_params[,4]),
            mean(other_hardwood_gaussian_params[,4]), mean(pine_gaussian_params[,4]),
            mean(spruce_gaussian_params[,4]), mean(tamarack_gaussian_params[,4]))
Range <- round(Range, digits = 3)
Range <- cbind(taxa, Range)
Range <- as.data.frame(Range)
Range <- tibble::column_to_rownames(Range, var = 'taxa')
knitr::kable(Range)
```

Based on these models and their range parameters, we can infer that grid cells approximately 5 away from each other are likely to be independent from one another. That is, we can sample every fifth grid cell to achieve spatial independence with reasonable confidence. It is important to note that this achieves spatial independence with respect to both the ecological processes of fossil pollen sediment settling, pollen dispersal, and tree range dynamics as well as the statistical process of borrowing strength across space. Therefore, it is not necessary to achieve full spatial independence for our analysis to be interesting and useful. 

Additionally, the spatial dependence in some taxa is likely to be low. We can look at this by computing the nugget:sill ratio:

```{r, echo = FALSE}
ash_NSR <- (ash_gaussian_params[,3]/ash_gaussian_params[,2])*100
beech_NSR <- (beech_gaussian_params[,3]/beech_gaussian_params[,2])*100
birch_NSR <- (birch_gaussian_params[,3]/birch_gaussian_params[,2])*100
elm_NSR <- (elm_gaussian_params[,3]/elm_gaussian_params[,2])*100
hemlock_NSR <- (hemlock_gaussian_params[,3]/hemlock_gaussian_params[,2])*100
maple_NSR <- (maple_gaussian_params[,3]/maple_gaussian_params[,2])*100
oak_NSR <- (oak_gaussian_params[,3]/oak_gaussian_params[,2])*100
other_conifer_NSR <- (other_conifer_gaussian_params[,3]/other_conifer_gaussian_params[,2])*100
other_hardwood_NSR <- (other_hardwood_gaussian_params[,3]/other_hardwood_gaussian_params[,2])*100
pine_NSR <- (pine_gaussian_params[,3]/pine_gaussian_params[,2])*100
spruce_NSR <- (spruce_gaussian_params[,3]/spruce_gaussian_params[,2])*100
tamarack_NSR <- (tamarack_gaussian_params[,3]/tamarack_gaussian_params[,2])*100

NSR <- c(mean(ash_NSR), mean(beech_NSR), mean(birch_NSR),
         mean(elm_NSR), mean(hemlock_NSR), mean(maple_NSR),
         mean(oak_NSR), mean(other_conifer_NSR), mean(other_hardwood_NSR),
         mean(pine_NSR), mean(spruce_NSR), mean(tamarack_NSR))
NSR <- round(NSR, digits = 3)
NSR <- cbind(taxa, NSR)
NSR <- as.data.frame(NSR)
NSR <- tibble::column_to_rownames(NSR, var = 'taxa')
knitr::kable(NSR)
```

From this, we can see that all taxa have a high degree of spatial dependence across our entire spatial domain of interest. Let's repeat this analysis, but remove the very low relative abundance of taxa that occurs outside of their range limits.

Here, I am doing the exact same procedure, but also filtering for relative abundance greater than a small value (specific to each taxon) that removes grid cells where the taxon is at very low abundance.

```{r, include = FALSE}
states <- map_states()
```

```{r, include = FALSE}
map_lon <- cbind(x_ind, x)
map_lat <- cbind(y_ind, y)
map_lon <- as.data.frame(map_lon)
map_lat <- as.data.frame(map_lat)
```

```{r}
p1 <- ash_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = ash)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Ash') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
# Abundant ash = > .25%
p2 <- ash_melt |>
  dplyr::filter(ash > 0.01) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = ash)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Ash') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
cowplot::plot_grid(p1, p2, nrow = 1)

ash_melt_red <- dplyr::filter(ash_melt, ash > 0.01)

ash_melt_red |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = ash)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void( )
```

```{r, echo = FALSE}
p1 <- beech_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = beech)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Beech') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
# Abundant beech = > 10%
p2 <- beech_melt |>
  dplyr::filter(beech > 0.1) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = beech)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Beech') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
cowplot::plot_grid(p1, p2, nrow = 1)

beech_melt_red <- dplyr::filter(beech_melt, beech > 0.1)

beech_melt_red |>
  dplyr::filter(time == 7) |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = beech)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void()
```

```{r, echo = FALSE}
p1 <- birch_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = birch)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Birch') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
p2 <- birch_melt |>
  dplyr::filter(birch > 0.1) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = birch)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Birch') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
cowplot::plot_grid(p1, p2, nrow = 1)

birch_melt_red <- dplyr::filter(birch_melt, birch > 0.1)

birch_melt_red |>
  dplyr::filter(time == 7) |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = birch)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void()
```

```{r, echo = FALSE}
p1 <- elm_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = elm)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Elm') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
p2 <- elm_melt |>
  dplyr::filter(elm > 0.1) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = elm)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Elm') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
cowplot::plot_grid(p1, p2)

elm_melt_red <- dplyr::filter(elm_melt, elm > 0.1)

elm_melt_red |>
  dplyr::filter(time == 7) |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = elm)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void()
```

```{r, echo = FALSE}
p1 <- hemlock_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = hemlock)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Hemlock') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
p2 <- hemlock_melt |>
  dplyr::filter(hemlock > 0.1) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = hemlock)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Hemlock') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
cowplot::plot_grid(p1, p2)

hemlock_melt_red <- dplyr::filter(hemlock_melt, hemlock > 0.1)

hemlock_melt_red |>
  dplyr::filter(time == 7) |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = hemlock)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void()
```

```{r, echo = FALSE}
p1 <- maple_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = maple)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Maple') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.4))
p2 <- maple_melt |>
  dplyr::filter(maple > 0.1) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = maple)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Maple') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.4))
cowplot::plot_grid(p1, p2, nrow = 1)

maple_melt_red <- dplyr::filter(maple_melt, maple > 0.1)

maple_melt_red |>
  dplyr::filter(time == 7) |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = maple)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void()
```

```{r, echo = FALSE}
p1 <- oak_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = oak)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Oak') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
p2 <- oak_melt |>
  dplyr::filter(oak > 0.1) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = oak)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Oak') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
cowplot::plot_grid(p1, p2, nrow = 1)

oak_melt_red <- dplyr::filter(oak_melt, oak > 0.1)

oak_melt_red |>
  dplyr::filter(time == 7) |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = oak)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void()
```

```{r, echo = FALSE}
p1 <- other_conifer_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = other_conifer)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Other conifer') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
p2 <- other_conifer_melt |>
  dplyr::filter(other_conifer > 0.1) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = other_conifer)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Other conifer') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
cowplot::plot_grid(p1, p2, nrow = 1)

other_conifer_melt_red <- dplyr::filter(other_conifer_melt, other_conifer > 0.1)

other_conifer_melt_red |>
  dplyr::filter(time == 7) |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = other_conifer)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void()
```

```{r, echo = FALSE}
p1 <- other_hardwood_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = other_hardwood)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Other hardwood') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
p2 <- other_hardwood_melt |>
  dplyr::filter(other_hardwood > 0.1) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = other_hardwood)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Other hardwood') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
cowplot::plot_grid(p1, p2, nrow = 1)

other_hardwood_melt_red <- dplyr::filter(other_hardwood_melt, other_hardwood > 0.1)

other_hardwood_melt_red |>
  dplyr::filter(time == 7) |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = other_hardwood)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void()
```

```{r, echo = FALSE}
p1 <- pine_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = pine)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Pine') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
p2 <- pine_melt |>
  dplyr::filter(pine > 0.2) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = pine)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Pine') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
cowplot::plot_grid(p1, p2, nrow = 1)

pine_melt_red <- dplyr::filter(pine_melt, pine > 0.2)

pine_melt_red |>
  dplyr::filter(time == 7) |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = pine)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void()
```

```{r, echo = FALSE}
p1 <- spruce_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = spruce)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Spruce') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
p2 <- spruce_melt |>
  dplyr::filter(spruce > 0.1) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = spruce)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Spruce') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
cowplot::plot_grid(p1, p2, nrow = 1)

spruce_melt_red <- dplyr::filter(spruce_melt, spruce > 0.1)

spruce_melt_red |>
  dplyr::filter(time == 7) |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = spruce)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void()
```

```{r, echo = FALSE}
p1 <- tamarack_melt |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = tamarack)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Tamarack') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
p2 <- tamarack_melt |>
  dplyr::filter(tamarack > 0.2) |>
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = tamarack)) +
  ggplot2::theme_minimal() +
  ggplot2::ggtitle('Tamarack') +
  ggplot2::theme(plot.title = ggplot2::element_text(size = 16, face = 'bold', hjust = 0.5))
cowplot::plot_grid(p1, p2, nrow = 1)

tamarack_melt_red <- dplyr::filter(tamarack_melt, tamarack > 0.2)

tamarack_melt_red |>
  dplyr::filter(time == 7) |>
  dplyr::rename(x_ind = x,
                y_ind = y) |>
  dplyr::left_join(y = map_lon, by = 'x_ind') |>
  dplyr::left_join(y = map_lat, by = 'y_ind') |>
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x = x, y = y, color = tamarack)) +
  ggplot2::geom_sf(data = states, color = 'black', fill = NA) +
  ggplot2::theme_void()
```

```{r, include = FALSE}
ash_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(ash_melt_red,
                       time == t,
                       !is.na(ash))

  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$ash,
                                model = 'gaussian', nb = 9)
  ash_red_params[i,1] <- t
  ash_red_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
beech_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(beech_melt_red,
                       time == t,
                       !is.na(beech))

  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$beech,
                                model = 'gaussian', nb = 7)
  beech_red_params[i,1] <- t
  beech_red_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
birch_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(birch_melt_red,
                       time == t,
                       !is.na(birch))
  
  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$birch,
                                model = 'gaussian', nb = 8)
  birch_red_params[i,1] <- t
  birch_red_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
elm_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(elm_melt_red,
                       time == t,
                       !is.na(elm))

  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$elm,
                                model = 'gaussian', nb = 9)
  elm_red_params[i,1] <- t
  elm_red_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
hemlock_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(hemlock_melt_red,
                       time == t,
                       !is.na(hemlock))

  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$hemlock,
                                model = 'gaussian', nb = 9)
  hemlock_red_params[i,1] <- t
  hemlock_red_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
maple_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(maple_melt_red,
                       time == t,
                       !is.na(maple))

  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$maple,
                                model = 'gaussian', nb = 6)
  maple_red_params[i,1] <- t
  maple_red_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
oak_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(oak_melt_red,
                       time == t,
                       !is.na(oak))

  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$oak,
                                model = 'gaussian', nb = 11)
  oak_red_params[i,1] <- t
  oak_red_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
other_conifer_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(other_conifer_melt_red,
                       time == t,
                       !is.na(other_conifer))

  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$other_conifer,
                                model = 'gaussian', nb = 10)
  other_conifer_red_params[i,1] <- t
  other_conifer_red_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
other_hardwood_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(other_hardwood_melt_red,
                       time == t,
                       !is.na(other_hardwood))

  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$other_hardwood,
                                model = 'gaussian', nb = 6)
  other_hardwood_red_params[i,1] <- t
  other_hardwood_red_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
pine_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(pine_melt_red,
                       time == t,
                       !is.na(pine))

  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$pine,
                                model = 'gaussian', nb = 5)
  pine_red_params[i,1] <- t
  pine_red_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
spruce_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(spruce_melt_red,
                       time == t,
                       !is.na(spruce))

  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$spruce,
                                model = 'gaussian', nb = 6)
  spruce_red_params[i,1] <- t
  spruce_red_params[i,2:4] <- sv$snr
}
```

```{r, include = FALSE}
tamarack_red_params <- matrix(, nrow = length(time), ncol = 4)

for(i in 1:length(time)){
  t <- time[i]
  sub <- dplyr::filter(tamarack_melt_red,
                       time == t,
                       !is.na(tamarack))

  sv <- geostats::semivariogram(x = sub$x, y = sub$y, z = sub$tamarack,
                                model = 'gaussian', nb = 9)
  tamarack_red_params[i,1] <- t
  tamarack_red_params[i,2:4] <- sv$snr
}
```

For this exercise, I individually determined a cutoff relative abundance that indicates that a taxon is meaningfully present. This cutoff was usually a relative abundance of 10% or greater, but could vary by taxon. The plots above show the density function of relative abundance for each taxon without filtering (left) and with filtering (right), as well as the geographic distribution of the taxon where it is meaningfully abundant.

Then, I refit semivariograms using the gaussian covariance function, which was shown to best fit the full data of each taxon above. I tuned the number of bins evaluated for each taxon because there was much more instability at large lag distances in the reduced datasets.

Here, I am reporting the range parameters when the taxon has an abundance greater than effectively zero (i.e., where the taxon is more likely to be present):

```{r, echo = FALSE}
taxa <- c('Ash', 'Beech', 'Birch',
          'Elm', 'Hemlock', 'Maple',
          'Oak', 'Other conifer', 'Other hardwood',
          'Pine', 'Spruce', 'Tamarack')
Range <- c(mean(ash_red_params[,4]), mean(beech_red_params[,4]),
            mean(birch_red_params[,4]), mean(elm_red_params[,4]),
            mean(hemlock_red_params[,4]), mean(maple_red_params[,4]),
            mean(oak_red_params[,4]), mean(other_conifer_red_params[,4]),
            mean(other_hardwood_red_params[,4]), mean(pine_red_params[,4]),
            mean(spruce_red_params[,4]), mean(tamarack_red_params[,4]))
Range <- round(Range, digits = 3)
Range <- cbind(taxa, Range)
Range <- as.data.frame(Range)
Range <- tibble::column_to_rownames(Range, var = 'taxa')
knitr::kable(Range)
```

Using this apporach, the average range of spatial dependence is approximately three grid cells. Based on this analysis, along with the visual inspection of spatial dependence of important taxa (pine, hemlock), I conclude that sammpling every three grid cells seems appropriate for our purpose.
